Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2014-11-11 paper/main.tex
compress the rules
cosmetics in the rules figure

\ifshort{
\small
{ \!\! B; R; (\Gamma, Q) \vdash \code{skip} \dashv (\Gamma, Q) \!!}
\and }{}
\Rule[leftskip=.2cm,rightskip=.1cm]{Q:Return}
{ B; (\Gamma_R,Q_R); (\Gamma_R[\Vret/x], Q) \vdash \code{return}~x \dashv (\Gamma',Q') }
\and \Rule[leftskip=.1cm,rightskip=.2cm]{Q:Update}
\\\\ B; R; (\Gamma', Q') \vdash S_2 \dashv (\Gamma'',Q'')
\iffull{\and

>>>>

\ifshort{
\begin{figure*}
\small
\begin{mathpar}
\Rule[leftskip=1.2cm,rightskip=.5cm]{Q:Ret}
{ P = Q_R[\Vret/x]
\\ \forall i \in \dom{P} . \, p_i = q_i
}
{ B; (\Gamma_R,Q_R); (\Gamma_R[\Vret/x], Q) \vdash \code{return}~x \dashv (\Gamma',Q') }
%
\and \Rule[leftskip=.5cm,rightskip=1.2cm]{Q:Update}
{ q'_{xy}, q'_{yx} \in \Qplusz
\\ \forall u. (q_{yu} = q'_{xu} + q'_{yu} \land q_{uy} = q'_{ux} + q'_{uy})
}
{ B; R; (\Gamma[x/y], Q {+} M_u {+} M_e(y)) \vdash x \gets y \dashv (\Gamma, Q') }
%
\\ \Rule[leftskip=.1cm,rightskip=.1cm]{Q:Loop}
{ (\Gamma', Q'); R; (\Gamma,Q) \vdash S \dashv (\Gamma,  Q {+} M_l) }
{ B; R; (\Gamma, Q) \vdash \code{loop}~S \dashv (\Gamma', Q') }
%
\and \Rule[leftskip=.2cm,rightskip=.1cm]{Q:IncP}
{ \Gamma \models y \ge 0 \!
\\ \mathcal U = \left\{ u \mid \Gamma \models x + y \in \inter x u \right\} \!
\\\\ \textstyle q'_{0y} = q_{0y}
      + \sum_{u \in \mathcal U} q_{xu}
      - \sum_{v \not\in \mathcal U} q_{vx} \!
}
{ \textstyle
  B; R; (\Gamma[x/x {+} y], Q {+} M_u {+} M_e(x {+} y)) \vdash x \gets x + y \dashv (\Gamma, Q')
}
%
\and \Rule[leftskip=1cm,rightskip=.5cm]{Q:DecP}
{ \Gamma \models y \ge 0
\\ \mathcal U = \left\{ u \mid \Gamma \models x - y \in \inter u x \right\}
\\\\ \textstyle q'_{y0} = q_{y0}
      + \sum_{u \in \mathcal U} q_{ux}
      - \sum_{v \not\in \mathcal U} q_{xv}
}
{ \textstyle
  B; R; (\Gamma[x/x {-} y],Q {+} M_u {+} M_e(x {-} y)) \vdash x \gets x - y \dashv (\Gamma, Q')
}
%
\and \Rule[leftskip=.5cm,rightskip=1cm]{Q:Inc}
{ M = M_u + M_e(x {\pm} y)
\\\\ \textstyle q'_{0y} = q_{0y} - \sum_{v} q_{vx}
\\ \textstyle q'_{y0} = q_{y0} - \sum_{v} q_{xv}
}
{ \textstyle
  B; R; (\Gamma[x/x {\pm} y], Q {+} M) \vdash x \gets x \pm y \dashv (\Gamma, Q')
}
%
\and \Rule{Q:If}
{ B; R; (\Gamma \land e, Q {-} M_c^1) \vdash S_1 \dashv (\Gamma',Q')
\\\\ B; R; (\Gamma \land \neg e, Q {-} M_c^2) \vdash S_2 \dashv (\Gamma',Q')
}
{ B; R; (\Gamma, Q{+}M_e(e)) \vdash \code{if}(e)~S_1~\code{else}~S_2 \dashv (\Gamma',Q') }
%
\and \Rule{Q:Seq}
{  B; R; (\Gamma, Q) \vdash S_1 \dashv (\Gamma', Q' {+} M_s)
\\\\ B; R; (\Gamma', Q') \vdash S_2 \dashv (\Gamma'',Q'')
}
{ B; R; (\Gamma, Q) \vdash S_1;S_2 \dashv (\Gamma'',Q'') }
%
\and\Rule{Q:Call}
{ (\Gamma_f, Q_f,  \Gamma_f', Q_f') \in \Delta(f) \!
\\ \text{Loc} = \text{Locals}(Q) \!
\\ \forall i \neq j . \, x_i \neq x_j \!
\\ c \in \Qplusz \!
\\ Q = P + S \!
\\ Q' = P' + S
\\ U = Q_f[\Vargs / \vec x]
\\ U' = Q'_f[\Vret/r]
\\ \forall i \in \dom{U} . \, p_i = u_i
\\ \forall i \in \dom{U'} .\, p'_i = u'_i
\\ \forall i \not\in \dom{U'} .\, p'_i = 0
\\ \forall i \not\in \text{Loc}
  .\, s_i = 0
}
{ B; R; (\Gamma_f[\Vargs / \vec x] \land \Gamma_{\text{Loc}}, Q {+} c {+} M_f)
  \vdash r \gets f(\vec x) \dashv
  (\Gamma_f'[\Vret/r] \land \Gamma_{\text{Loc}}, Q' {+} c {-} M_r)
}
%
\and
\Rule[leftskip=.2cm,rightskip=.2cm]{Q:Extend}
{ \fenv f = (\vec y, S_f)
\\\\ B; (\Gamma_f', Q'_f); (\Gamma_f[\Vargs/\vec y], Q_f[\Vargs/ \vec y] ) \vdash S_f \dashv (\Gamma', Q')
}
{ (\Gamma_f, Q_f, \Gamma_f', Q_f') \in \Delta(f) }
%
\and \Rule{Q:Weak}
{ B; R; (\Gamma_2,Q_2) \vdash S \dashv (\Gamma'_2, Q'_2)
\\ \!\! \Gamma_1 \models \Gamma_2
\\\\ Q_1 \succeq_{\Gamma_1} Q_2
\\ \Gamma'_2 \models \Gamma'_1
\\ Q'_2 \succeq_{\Gamma_2'} Q'_1
}
{ B; R; (\Gamma_1,Q_1) \vdash S \dashv (\Gamma'_1, Q'_1) }
%
\and \Rule{Relax}
{ \mathcal L = \{ xy \mid \exists l_{xy} {\in} \N \, . \, \Gamma \models l_{xy} \le |\inter x y| \}
\\ \mathcal U = \{ xy \mid \exists u_{xy}{\in} \N \, . \, \Gamma \models |\inter x y| \le u_{xy} \}
\\\\ \forall i \in \mathcal U.\, q'_i \ge q_i - r_i
\\ \forall i \in \mathcal L.\, q'_i \ge q_i + p_i
\\ \forall i \not\in \mathcal U {\cup} \mathcal L {\cup} \{0\} .\, q'_i \ge q_i
\\ q'_0 \geq q_0 {\textstyle + \sum_{i \in \mathcal U} u_i r_i - \sum_{i \in \mathcal L} l_i p_i}
}
{ Q' \succeq_\Gamma Q }
